A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-16 survey.tex
Fixing author name typo

\author{Santiago~Onta\~{n}\'{o}n\thanks{Santiago~Onta\~{n}\'{o}n is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Gabriel~Synnaeve\thanks{Gabriel~Synnaeve is with the Laboratory of Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm in Paris, France.},
        Alberto~Uriarte\thanks{Alberto Uriarte is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Florian~Richoux\thanks{Florian~Richoux is with the Laboratory of Computer Science of the University of Nantes, France.},
        Dave~Churchill\thanks{Dave~Churchill is with the Computing Science Department of the University of Alberta, Edmonton, Canada.},
        Mike~Preuss\thanks{Mike~Preuss is with the Department of Computer Science of Technische Universit{\"a}t Dortmund, Germany.}}

>>>>

\author{Santiago~Onta\~{n}\'{o}n\thanks{Santiago~Onta\~{n}\'{o}n is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Gabriel~Synnaeve\thanks{Gabriel~Synnaeve is with the Laboratory of Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm in Paris, France.},
        Alberto~Uriarte\thanks{Alberto Uriarte is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Florian~Richoux\thanks{Florian~Richoux is with the Laboratory of Computer Science of the University of Nantes, France.},
        David~Churchill\thanks{David~Churchill is with the Computing Science Department of the University of Alberta, Edmonton, Canada.},
        Mike~Preuss\thanks{Mike~Preuss is with the Department of Computer Science of Technische Universit{\"a}t Dortmund, Germany.}}
